---
title: "Seqinr"
author: "Fatima Mawassi
         Nathalia Gomide Cruz"
date: "2023-12-05"
output: pdf_document
---
```{r}

```

Install et load "seqinr":
```{r}
install.packages("seqinr")
library("seqinr")
```

Ask for more information about a particular R command by using the help() function:
```{r}
??seqinr
library(help=seqinr) 
```

Retrieving genome sequence data using SeqinR:

Exemple:Borrelia burgdorferi genome sequence, which has NCBI accession "AC=CP000013", from the NCBI website.
```{r}
getncbiseq <- function(accession)
choosebank("genbank")
```


Query: To get the sequence number and the list of sequence names from an ACNUC data base located on the web

SP=taxon seqs attached to taxon or any other below in tree; @ wildcard possible:
```{r}
bb_sp <- query("bb", "sp=Borrelia burgdorferi")
print (bb)
```

AC=accessionno seqs attached to specified accession number:
```{r}
bb_accession <- query("bb", "AC=CP000013")
print (bb)
```


To get the names of the 1 and 4 first sequences:
```{r}
sapply(bb_accession$req[1], getName)
sapply(bb_sp$req[1:4], getName)
```

To get the 4 first sequences:
```{r}
seq_comp = sapply(bb_accession$req[1], getSequence, as.string = TRUE)
sapply(bb_sp$req[1:4], getSequence, as.string = TRUE)
```

To get the 50 nucleotides of the Borrelia burgdorferi sequence:
```{r}
seq <- getSequence(bb_accession$req[[1]])
print(seq[1:50])
```
 

Writing sequence data out as a FASTA file = save sequence:
```{r}
write.fasta(names="BORBUR", sequences=seq, file.out="borbur.fasta")
```

Reading sequence data into R:
```{r}
borrelia <- read.fasta(file = "borbur.fasta")
borrelia

borrelia_seq <- borrelia[[1]]
borrelia_seq
```

Length of a DNA sequence:

```{r}
getLength(borrelia_seq)
```

Base composition of a DNA sequence:

```{r}
table(borrelia_seq)
```


GC Content of DNA: One of the most fundamental properties of a genome sequence is its GC content, the fraction of the sequence that consists of Gs and Cs, ie. the %(G+C).

```{r}
GC(borrelia_seq)
```

DNA words: To find the number of occurrences of DNA words of a particular length, we can use the count() function from the R SeqinR package.

```{r}
count(borrelia_seq, 4
      )
```

```{r}
heights <- table(borrelia_seq)
barplot(heights, main = "Composition en base", xlab = "Base", ylab = "Fréquence", col = c("skyblue", "red", "green", "purple"))
```




